\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.55in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=*, topsep=1pt, itemsep=0pt, parsep=0pt, partopsep=0pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{5pt}{3pt}

\begin{document}

{\LARGE \textbf{Stefan Dorosh}} \hfill Vancouver, BC \\
Full-Stack Web Developer \\
\href{mailto:stefandorosh24@gmail.com}{stefandorosh24@gmail.com} \;|\; 604-977-1604 \;|\;
\href{https://stefandorosh.com}{stefandorosh.com} \;|\;
\href{https://github.com/SDX24}{github.com/SDX24} \\
\href{https://gitlab.com/SDX24}{gitlab.com/SDX24} \;|\;
\href{https://linkedin.com/in/stefan-dorosh}{linkedin.com/in/stefan-dorosh}

\section*{Summary}
Product-minded full-stack developer focused on TypeScript/Next.js applications, secure auth/session workflows, and relational data design. Experience across live company platforms and large-scale academic product builds.

\section*{Technical Skills}
\textbf{Languages:} TypeScript, JavaScript, SQL, C\#, HTML, CSS/Sass, PHP \\
\textbf{Frameworks/Libraries:} React, Next.js, Node.js, Express, Socket.IO, Drizzle ORM, Prisma, Clerk, Tailwind CSS \\
\textbf{Data/Infra:} PostgreSQL, MySQL, MongoDB, REST APIs, CI/CD, multi-tenant SaaS, object storage (S3-style) \\
\textbf{Engineering:} Auth/session security, i18n localization, SEO strategy, Lighthouse optimization, AI API integration \\
\textbf{Tools:} Git, GitHub, GitLab, GitHub Actions, VS Code, Linux, AWS, Vercel, Render, Jira, Trello, Figma

\section*{Selected Technical Work}
\textbf{RUDI} \hfill \href{https://rudi.asia}{rudi.asia} \\
\textit{Full-Stack Developer Intern} \hfill Jan 2026 -- Apr 2026 \\
\begin{itemize}
  \item Built features in a production Next.js App Router platform for long-term housing discovery, working within established architecture and release constraints.
  \item Implemented API-integrated product flows and localization (i18n) across listing, discovery, and account experiences.
  \item Improved performance and UX with Lighthouse-driven optimization, lazy-loading strategies, and page-level reformatting across key user flows.
  \item Strengthened SEO and technical foundations with metadata, manifest updates, React component refactors, and iterative Agile bug-fix cycles.
\end{itemize}

\textbf{Vero Ventures | InsurFlow} \hfill \href{https://insurflow.biz}{insurflow.biz} \;|\; \href{https://github.com/Vero-Ventures/insurflow}{GitHub} \\
\textit{Full-Stack Developer Intern} \hfill Jan 2026 -- Apr 2026 \\
\begin{itemize}
  \item Rebuilt a greenfield InsurTech SaaS in a team of 5 using Next.js, TypeScript, PostgreSQL, and Drizzle ORM for a modern multi-tenant foundation.
  \item Developed advisor-facing calculation and dashboard features; integrated AI-assisted workflows using OpenAI APIs for faster, data-driven operations.
  \item Implemented DevOps and CI/CD guardrails using GitHub Actions with Vercel preview and production deployment flows.
\end{itemize}

\textbf{Tandem} \hfill \href{https://tandem-app.com}{tandem-app.com} \;|\; \href{https://github.com/IDSP-TRADECARE/Tandem}{GitHub} \\
\textit{Lead Full-Stack Developer (Academic Industry Project)} \hfill Sep 2025 -- Dec 2025 \\
\begin{itemize}
  \item Built a collaborative scheduling platform with secure authentication, complex user roles, and reliable multi-user access/session flows.
  \item Designed typed Socket.IO event contracts to power real-time sharing parties, live chat, and synchronized scheduling interactions.
  \item Implemented AI-assisted pipelines that transformed voice, text, and PDF inputs into structured scheduling-ready application data via API integrations.
\end{itemize}

\section*{Additional Experience}
\textbf{W3rlds} | UI/UX Web Designer Intern (Remote) \hfill Aug 2024 \\
Designed layouts in Figma/Framer, improved usability from feedback, and supported SEO-oriented content structure. \\
\textbf{Platform 7 Coffee} | Barista \hfill Jul 2025 -- Mar 2026 \\
Delivered fast customer service, handled POS operations, and coordinated effectively in high-traffic team shifts.

\section*{Education}
\textbf{British Columbia Institute of Technology (BCIT)} \hfill Sep 2024 -- May 2026 \\
Diploma, Full-Stack Web Development \\
\textbf{Canggu Community School} \hfill Sep 2021 -- May 2024 \\
International Baccalaureate Diploma Programme

\end{document}
